### 2017-09-14 Writing/draft.tex
Updated results
Abstract thoughts

@@

%---------------------------------------------
% LaTeX tips for modifying/editing the document:
%---------------------------------------------
% - You can comment using the percentage sign. I suggest you use the % sign alone for commenting out sections of the text:
%       e.g. "This is a really long sentence %because this sentence is very long." Here the % is used for ignoring the end of the sentence (but for some reason you want to keep track of it).%
%       For comments as in verbose comments, I suggest you use "%MB:":
%       e.g. "This is a really long sentence %because this sentence is very long. %MB: yeah, no shit!" 
% - For optimal version control, write only one sentence per line (for more precise track changes)
% - To build the pdf, use command+B in Sublime.
% - Because of the bibliography, the pdf needs to be build in the same folder that contains "References.bib" and "sysbio.bst"
% - For citing papers, you must put their bibtex reference in the "References.bib" file and then you can use the following sysbio tags:
%        \cite{bibtexBob2000} for citing within a sentence: "Bob (2000)"
%        \citep{bibtexBob2000} for citing within brackets: "(Bob, 2000)"
%        \citep[Before:][-After]{bibtexBob2000} for citing within brackets with additional text: "(Before: Bob, 2000 -After)"
%        \citealt{bibtexBob2000} for citing without brackets: "Bob, 2000"
%        You can put more cites in each \cite tag by separating them with commas.
% - For equation, find every details here: https://en.wikibooks.org/wiki/LaTeX/Mathematics
% - For titles and stuff, the hierarchy goes \section{}, \subsection{}, \subsubsection{} and so forth...
% - For bullet points or enumerations you can use:
%       \begin{itemize}
%           \item my first bullet point/enumeration
%       \end{itemize}
%       With replacing "itemize" by "enumerate" for enumeration.

@@

\begin{itemize}
    \item \textbf{Biological induce dependence between characters:} this is the result of a link between two characters through development and/or biological function.
    These links are readily understood through developmental biology or understanding of shared function between features \citep{goswami2006morphological,goswami2010,goswami2014macroevolutionary}.
    One trivial example would be the link between lower and upper molar characters in mammals: one character describing a feature of a lower molar will be expected to be correlated to another character describing another feature of the associated upper molar.

@@

    \item \textbf{Coding induced dependence between characters:} this is the results of researchers methodology for defining or/and coding discrete morphological characters \citep{Brazeau2011,simoes2017giant}.
    These links can be due to methodological errors: for example one could define a character describing a particular feature on a left molar as well as another character describing the same feature on a right molar.
    It is worth noting, however, that these dependences could also be due to the nature of the available data, especially in palaeontology.
    For example, when only one fragmentary molar is available to describe a specimen, researchers have to ``extract'' as much phylogenetic information from the available data as possible, potentially inducing correlations.
\end{itemize}

>>>>

The project implies inferring a total of 2880 phylogenetic trees (40 replicates of 9 data combination scenarios generating 4 trees each; both inferred in Bayesian and under Maximum Parsimony).
The calculations for the project is ongoing since December 2016 a and is now 95.27\% completed (with a current cumulated computational time of around 80 CPU years that generated 3.2 TB of trees).
The pipelines for analysing the data and producing the publishable figures and tables is already implemented and most of the manuscript is already written ()

Overall we found a positive effect of reducing character correlations on recovering the correct topology.
However, this effect is less important for matrices with a small number of taxa (~25) were reducing character correlation was not more effective than randomly drawing characters.
Furthermore, in bigger matrices (~350 taxa), there is a strong effect of the inference method with Bayesian trees being consistently less affected by character correlation than maximum parsimony trees.

These results suggest that ignoring the problem of character correlation or independence can easily impact topology in phylogenetic analysis.
However, encouragingly, they also suggest that, unless correlation is effectively maximised or minimised, probabilistic methods can easily accommodate for random correlation between characters.

@@

@@

\begin{itemize}

    %TG: Change this induced thing

    \item \textbf{Biological induce dependence between characters:} this is the result of a link between two characters through development and/or biological function.
    These links are readily understood through developmental biology or understanding of shared function between features \citep{goswami2006morphological,goswami2010,goswami2014macroevolutionary}.
    One trivial example would be the link between lower and upper molar characters in mammals: one character describing a feature of a lower molar will be expected to be correlated to another character describing another feature of the associated upper molar.

@@

    %TG: This one can be reworded. Get a dichotomie a priori/a posteriori correlation. + add trade off in coding (more characters = more info but less independence)
    \item \textbf{Coding induced dependence between characters:} this is the results of researchers methodology for defining or/and coding discrete morphological characters \citep{Brazeau2011,simoes2017giant}.
    These links can be due to methodological errors: for example one could define a character describing a particular feature on a left molar as well as another character describing the same feature on a right molar.
    It is worth noting, however, that these dependences could also be due to the nature of the available data, especially in palaeontology.
    For example, when only one fragmentary molar is available to describe a specimen, researchers have to ``extract'' as much phylogenetic information from the available data as possible, potentially inducing correlations.
\end{itemize}
